project 1

### 2017-01-12 project_1.Rmd
added conclusion slides and other stuff

```{r, message=FALSE, warning=FALSE, results="hide"}
prostate <- read_excel("~/Downloads/Prostate SBRT Sexual Function Data.xlsx", skip = 7)
prostate <- data.table(prostate)
prostate <- prostate[complete.cases(prostate)] # remove last row which is empty
# Code ADT as numeric; Y = 1, N = 0
prostate[ADT == "Y", ADT := 1]
prostate[ADT == "N", ADT := 0]
prostate[, ADT := as.numeric(ADT)]
```

@@

## Exploratory Data analysis
### Histograms
```{r, message=FALSE, warning=FALSE}
age_hist <- ggplot(data = prostate, aes(x = Age)) + 
  geom_histogram()
psa_hist <- ggplot(data = prostate, aes(x = PSA)) + 
  geom_histogram()
hrqol_hist <- ggplot(data = prostate, aes(x = HRQOL)) + 
  geom_histogram()
bmi_hist <- ggplot(data = prostate, aes(x = BMI)) + 
  geom_histogram()
grid.arrange(age_hist, psa_hist, hrqol_hist, bmi_hist, ncol = 2)
```

@@

### Logistic Regression
```{r}
prostate_logreg <- glm(`Erectile Function at 2 years` ~ Age + `Gleason Score` + `T-Stage Group` + PSA + HRQOL + ADT + BMI + `Erectile Function at Baseline`, family = binomial(link = "logit") ,data = prostate)
# summary(prostate_logreg)
kable(tidy(prostate_logreg))
prostate <- prostate[, predicted_prob := predict(prostate_logreg)]
prostate <- prostate[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- prostate[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate

```
```{r, results = "asis"}
stargazer(prostate_logreg, header = F, type = "latex")
```

@@

>>>>

```{r, message=FALSE, warning=FALSE, results="hide"}
prostate <- read_excel("~/Downloads/Prostate SBRT Sexual Function Data.xlsx", skip = 7)
prostate <- data.table(prostate)
prostate <- prostate[complete.cases(prostate)] # remove last row which is empty
# Code ADT as numeric; Y = 1, N = 0
prostate[ADT == "Y", ADT := 1]
prostate[ADT == "N", ADT := 0]
prostate[, ADT := as.numeric(ADT)]
prostate[, centered_age := Age - mean(Age)]
```

@@

## Exploratory Data analysis
### Histograms
```{r, message=FALSE, warning=FALSE}
age_hist <- ggplot(data = prostate, aes(x = Age)) + 
  geom_histogram()
psa_hist <- ggplot(data = prostate, aes(x = PSA)) + 
  geom_histogram()
hrqol_hist <- ggplot(data = prostate, aes(x = HRQOL)) + 
  geom_histogram()
bmi_hist <- ggplot(data = prostate, aes(x = BMI)) + 
  geom_histogram(fill = "red")
bmi_hist
grid.arrange(age_hist, psa_hist, hrqol_hist, bmi_hist, ncol = 2)

bmi_boxplot <- ggplot(data = prostate, aes(x = 0, y = BMI)) + 
  geom_boxplot(color = "blue", outlier.color = "red")
bmi_boxplot
```

@@

### Logistic Regression
```{r}
prostate_logreg <- glm(`Erectile Function at 2 years` ~ Age*PSA + `Gleason Score` + `T-Stage Group` + PSA + HRQOL + ADT + BMI + `Erectile Function at Baseline`, family = binomial(link = "logit"), data = prostate)
summary(prostate_logreg)

# edit results table
prostate_logreg_results <- data.table(tidy(prostate_logreg))
prostate_logreg_results[, lower := exp(estimate - std.error)]
prostate_logreg_results[, OR := exp(estimate)]
prostate_logreg_results[, upper := exp(estimate + std.error)]
kable(prostate_logreg_results[, .(term, lower, OR, upper, p.value)], digits = 2)

# calculate error rate
prostate <- prostate[, predicted_prob := predict(prostate_logreg, type = "response")]
prostate <- prostate[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- prostate[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate

```
# Manually create small prostate table for example predictions
```{r}
example_prostate <- data.table(Age = 69, "Gleason Score" =  7, "T-Stage Group" = 0, "PSA" = 7.7, 
                               HRQOL = 56, ADT = 0, BMI = 29, "Erectile Function at Baseline" =  1)
example_prostate <- example_prostate[, probability_of_function := predict(prostate_logreg, example_prostate, type = "response")]
example_prostate <- example_prostate[, predicted_function := ifelse(probability_of_function >= 0.5, 1, 0)]
```

```{r, results = "asis"}
stargazer(prostate_logreg, header = F, type = "latex")
```

@@

# Base guessing
```{r}
sub_logreg <- glm(`Erectile Function at 2 years` ~ PSA + HRQOL + Age + `Erectile Function at Baseline`, family = binomial(link = "logit"), data = prostate)
kable(tidy(sub_logreg))

# calculate error rate
prostate <- prostate[, predicted_prob := predict(sub_logreg)]
prostate <- prostate[, predicted := ifelse(predicted_prob >= 0.5, 1, 0)]
error_rate <- prostate[, sum(abs(predicted - `Erectile Function at 2 years`))]/dim(prostate)[1]
error_rate
```
